Considering scale in multilayer animal social networks

### 2020-06-13 paper/manuscript.Rmd
reorg mv temp above nobs
start temp
tidy, rm

@@

Some multilayer network metrics were strongly influenced by the length of the
time window. Mean graph strength was weak but became slightly stronger with
increasing time window length during the summer, but the higher mean graph
strength during the winter showed a slight increase then decrease with
increasing winter length (Figure \@ref(fig:winlen)a). Layer relevance increased
for all summer layers as individuals became more connected with increasing
window lengths, but winter layers showed relatively stable but high layer
relevance (Figure \@ref(fig:winlen)b). This pattern indicates that the
proportion of neighbours that were the same across layers increased with a
longer time frame during the summer, but there were a high proportion of
neighbors that remained the same across layers during the winter, regardless of
time length. Furthermore, though the layers were generally not very similar
between the summer and winter, the length of the time window created slight
variability in this metric, particularly for forage and open habitat types
(Figure \@ref(fig:winlen)c). Connective redundancy increased marginally with
increasing window length, indicating that the proportions of neighbours that
were the same across layers, though relatively high in general, slightly
increased when time length was greater (Figure \@ref(fig:winlen)d). These
results suggest that an increasing window length, especially for the summer
season, may be resulting in less precisely defined seasons that are not clearly
capturing periods of aggregation and dissaggregation related to resource
availability.

Moving window positions defining seasons showed some dramatic changes in the
multilayer network metrics as the seasons were redefined. Graph strength
increased at time window position ~20 for summer and winter layers and, while
summer layers continued to increase, winter layers showed a decrease in graph
strength at time window position ~35 (Figure \@ref(fig:winpos)a). Layer
relevance increased across moving window positions for summer layers and
slightly decreased for winter layers (Figure \@ref(fig:winpos)b). These results
indicate increased connectivity in summer layers and slightly decreasing
connectivity at shifted winter time windows. Layer similarity was relatively
stable across moving window positions except for a sharp decline at window
position ~28 in forage and open layers (Figure \@ref(fig:winpos) c). Connective
redundancy showed a marginal increase with increasing window position indicating
individuals had more of the same neighbours in each habitat network (Figure
\@ref(fig:winpos) d). Similar to window length, changing the position of the
time window in this case results in a mismatch between expected periods of
resource seasonality and corresponding sociality, particularly for the summer,
highlighting the importance of carefully selecting temporal scale of analysis.

@@

<!-- Figure: Window length -->
(ref:temp) Varying temporal scale in multilayer networks.  
Multilayer networks were generated of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected in time window 1, 6-11, and 15-20, compared to 2-5 and 12-15. C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.

<!-- a bit more for g strength? -->

>>>>

The ordinal multilayer network generated from discrete time windows indicated 
within-year periods of increased caribou sociality. Edge overlap

(Figure \@ref(fig:temp) )
These
results suggest that an increasing window length, especially for the summer
season, may be resulting in less precisely defined seasons that are not clearly
capturing periods of aggregation and dissaggregation related to resource
availability.

changing the position of the
time window in this case results in a mismatch between expected periods of
resource seasonality and corresponding sociality, particularly for the summer,
highlighting the importance of carefully selecting temporal scale of analysis.

@@

@@

<!-- Figure: Time window -->
(ref:temp) Varying temporal scale in multilayer networks. Multilayer networks were generated of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected in time window 1, 6-11, and 15-20, compared to 2-5 and 12-15. C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.

<!-- TODO: a bit more for g strength? -->
